### 2024-07-07 causal-inference.qmd
20240707 - quasi-experimental designs

>>>>

We cannot directly test or establish causality from a non-experimental research design.
Nevertheless, we can leverage various design features that, in combination with other studies using different research methods, collectively strengthen our ability to make causal inferences.
For instance, there are are no experiments in humans showing that smoking causes cancer—randomly assigning people to smoke or not smoke would not be ethical.
The causal inference that smoking causes cancer was derived from a combination of experimental studies in rodents and observational studies in humans.
